---
title: "the motivating use-case for simeta::"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
params: 
  trials: 3
---

```{r, include = FALSE}
knitr::opts_chunk$set(cache = TRUE)

```

### Important message for future Charles: 

**Remember, writing this provides a fun and aesthestic way of debugging this algorithm. Focus on writing a cohesive document, and the debugging  will be enjoyable. It's a cognitive bait and switch; and it works. Make the document _pretty_, and you not be able to help ensuring the science is correct, because you hate doing a sloppy job at anything. Answer the question, with clarity and aesthetics; the motivation for correct science will follow.**

## preamble

```{r setup}
library(simeta)

# other packages used in this vignette
library(tidyverse)
library(skimr)

# otherwise i'll forget
conflicted::conflict_prefer("filter", winner = "dplyr")

# for reproducibility
set.seed(39)

```

# Objective of the `simeta::` package

The `simeta::` package aims to provide coverage probability simulation results for estimators derived, as is common in meta-analyses, from summary statistics for the variance of the sample median. 


Different simulation-level parameters of interest can be specified so that simulated data mimics different meta-analytic conditions:

- Different numbers of $K$ studies.
- Different values of $\tau^2$, the variation between the studies.
- Different distributions.
- Different distributions of expected sample sizes.
- Different proportions of control and intervention group.

The components of the algorithm have been produced in a compartmentalised way, with the objective of exploring the extendability of this package to estimators for the variance of the sample mean, but also for estimators for the mean or median, themselves.   

In this vignette, we restrict ourselves to the original use-case of the package, testing estimators for the variance of the sample median.

# Using `simeta::` to assess an estimator for the sample median

In this analysis, we are interested in assessing how an estimator for the variance of the sample median performs in under various meta-analytic conditions.

We will test estimators provided by `varameta::` package. 

For example, given a sample median of 50, an interquartile range of 0.6, and a sample size of 24, what do we estimator the variance of the sample median to be? 

```{r median var}

varameta::effect_se(
  centre = 50, 
  spread = 0.6, 
  n = 24, 
  centre_type = "median",
  spread_type = "iqr") 

```

How can we tell if this is a *good* estimator for the variance of the sample median?

Well, if have the true median $\nu$ and the true distribution $f$, we can approximate the variance of the sample median by adapting the following result, (todo: cite) 
$$
\textrm{var}(M) \approx \frac 1 {4nf(\nu)^2}.
$$
to ,
todo: eqn.

todo: medians ms & varmeta discuss connection

```{r metasims defaults}

# metasims function with default arguments
sims <-
  metasims(
    single_study = FALSE,
    measure = "median",
    measure_spread = "iqr",
    distributions = default_parameters,
    k = c(3, 7, 10),
    tau_sq_true = seq(from = 0, to = 0.4, by = 0.2),
    unequal_effect_ratio = 1.2,
    min_n = 20,
    max_n = 200,
    prop = 0.5,
    prop_error = 0.1,
    trials = params$trials,
    trial_fn = metatrial,
    beep = FALSE,
    knha = TRUE,
    progress = FALSE
  ) 

# take a look at results
sims %>% pluck("results") %>% head()

```

```{r coverage plot, out.width="\\textwidth"}
 
# basic scatterplot
sims %>% 
  coverage_plot()

```

# Components of simeta

The central motivation to modularising this package is attempting to address how to create extendable research analyses. Perhaps not all of the solutions provided are of use, but perhaps some components are. 

In this section we describe the different classes of functions in the `simeta::` package.

todo: briefly describe each 

## Simulation-level parameters

The `metasims` function has a set of default simulation-level parameters, `default_parameters`. In the [following section](#specify-dist) it is shown how to specify these parameters. 


```{r metasims args}

# extract default arguments of simulation function
args(metasims)

# arguments are easier to read and extract using the output of the simulation object
# todo: convert to function
# this simulation used the same as the default arguments
sims %>% 
  pluck("arguments") %>% 
    kableExtra::kable() %>% 
  kableExtra::kable_styling()

```

In the above table, we set simulation-level parameters:

argument | description 
- | -
`single_study` | Is there only one study? i.e., $k = 1$.
`measure` | Measure of effect: `"median"` or `"mean"`
`measure_spread`| Measure of spread: `"iqr"` or `"range"`.
`k` | Number of studies.

> todo: finish table
> todo fiish desription of table
> finish what comes after that

The distributions sampled are expected to be in the form of a table, with one column for distributions `dist` in an R-friendly format, and parameters `par` in a list. 

```{r default parameters}
# simeta comes with a default parameter set
default_parameters %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()

```


### Specifying distribution parameters {#specify-dist}

You can specify your 

It is expected to be of the form of a `tibble` with a column, `dist`, for R-friendly distribution names and a column, `par`. R-friendly means by concatenating on `d`, `p`, `q`, or `r`, you obtain a distribution function in R. 

```{r default parameters vis}
sims %>%
  pluck("distributions") %>% 
  sim_dist(output = "table")

sims %>% 
  pluck("distributions") %>% 
  sim_dist()

```

The `simeta::` package is currently coded to simulate date from the normal, exponential, Pareto, and log-normal distributions. 

The mathematical methodology to is repeated, but the derivation is slightly different.

For these distributions, any reasonable parameter choice can be specified via the `par` column. 

## Research output tools

Simeta provides a few research outputs, which we describe in this section: 

1. Coverage plot
2. Distributions sampled summary tools
3. Simulation results as data

### Coverage plot

The coverage probability plot summarises the proportion of trials for each metaparameter set of distribution, variation between studies, effect ratio, and number of studies.  

```{r }
sims %>% 
  coverage_plot()

```

### Distributions summary

There are three ways to summarise the distributions sampled in the simulation:

1. Plot
2. Table
3. R dataframe

```{r}
# plot
sims %>% 
  pluck("distributions") %>% 
  sim_dist()

# table
sims %>% 
  pluck("distributions") %>% 
  sim_dist(output = "table")

# data.frame
sims %>% 
  pluck("distributions")

```


### Simulation results

A list-object is returned from `metasims` that provides: 

1. simulation results in a tibble
2. simulation metaparameters in a summary tibble
4. simulation metaparameters, one row per simulation
3. simulation distributions 

```{r}

# metasims-created object
sims %>% str(1)

# simulation results
sims %>% pluck("results") %>% skimr::skim()

# simulation metaparameters summary
sims %>% pluck("arguments") %>% 
  kableExtra::kable() %>% kableExtra::kable_styling()


# simulation metaparameters, one row per simulation
sims %>% pluck("sim_pars") %>% head() %>% select(1:5) %>% 
  kableExtra::kable() %>% kableExtra::kable_styling()

# simulation distributions summary
sims %>% pluck("distributions") %>% 
  kableExtra::kable() %>% kableExtra::kable_styling()

```

## Simulation tools

The components of `simeta::` are deliberately modularised, with the intention of facilitating future optimisation and improvements.

