---
title: "Simulation tools in the `simeta::`"
output: 
  html_document:
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(varameta)
library(simeta)

```

# `simeta::` components overview

- todo: overview of simeta components

```{}
# input
simulation parameters %>%
  # function
  simulations | function %>% 
    simulation parameters | dataframe %>% 
      simulation trial | per row x |trials| %>% 
      trial results | dataframe %>% 
    simulation results | mutate %>% 
  # output a dataframe summarising results
  simulations results | dataframe
  
```

# Simulation metaparameters

# Trial: The atom of a metasimulation toolchain

A trial function in `simeta::` takes takes a set of simulation parameters, samples data, estimates an overall effect of interest, and outputs a summary. 

# Simulation: An analysis of trials

```{r}
metatrial()


```


# Metasimulation: An analysis of simulations

A metasimulation is a collection of simulations.  The `metasim()` function 

```{r}
metasim()
```


# Simulation output
